Use of significance test logic by scientists in a novel reasoning task

### 2020-05-21 inst/manuscript/manuscript.Rmd
fixed issue with pandoc compilation of vignettes

bibliography: "`r system.file('bib/bibfile.bib', package = 'MoreyHoekstra2019')`"

@@

As Table \ref{tab:strategies} shows that a large majority of participants (`r for_table[1,1]`, `r round( 100*as.numeric(for_table[1,1]) / as.numeric(for_table[1,6]), 2)`%) indicated using strong significance testing strategies. We should be cautious, however, because participants were told in the instructions that the shuffle reports could be used for assessing sampling variability. We did this to make clear what the shuffle reports were, but without explaining how to use them. To some extent, then, the text responses may reflect the instructions. However, the data strongly suggest a deeper understanding; first, among the responses were richer, lucid descriptions of SST logic, such as:

@@

The instructions did not tell the participants *how* they should use the shuffles reports, yet many participants gave detailed accounts. Moreover, as we show next, participants' decisions were sensitive to a key manipulation of the shuffles reports in the manner that one would expect if they were using SST logic.

>>>>

bibliography: "``r system.file('bib/bibfile.bib', package = 'MoreyHoekstra2019')``{=latex}"

@@

As Table \ref{tab:strategies} shows that a large majority of participants (`r for_table[1,1]`, `r round( 100*as.numeric(for_table[1,1]) / as.numeric(for_table[1,6]), 2)`%) indicated using strong significance testing strategies. We should be cautious in directly interpreting this high number alone, however, because participants were told in the instructions that the shuffle reports could be used for assessing sampling variability. We did this to make clear what the shuffle reports were, but without explaining how to use them. To some extent, then, the text responses may reflect the instructions. However, the data strongly suggest a deeper understanding; first, among the responses were richer, lucid descriptions of SST logic, such as:

@@

Secondly---and most importantly---the instructions did not tell the participants *how* they should use the shuffles reports, yet many participants gave detailed accounts. As we show next, participants' decisions were sensitive to a key manipulation of the shuffles reports in the manner that one would expect if they were using SST logic.
